---
title: "p8105_hw1_sdc2157"
author: "Stephanie Calluori"
date: 2023-09-23
output: github_document
---

```{r}
library(moderndive)
library(tidyverse)
```

# Problem 1

For this exercise, we will be examining the early_january_weather dataset, which catalogs hourly weather data for LGA, JFK, and EWR airports during January 2013. 

```{r}
data("early_january_weather")

```

The data set contains `r nrow(early_january_weather)` observations and `r ncol(early_january_weather)` variables. Variables include `r colnames(early_january_weather)` . 

Next, we will examine some key variables.

```{r}
temp_vec <- pull(early_january_weather, temp)
wind_speed_vec <- pull(early_january_weather, wind_speed)
visib_vec <- pull(early_january_weather, visib)
```

The average temperature was `r round(mean(temp_vec), digits = 1)` degrees F with a standard deviation of `r round(sd(temp_vec), digits = 1)`degrees F. The minimum and maximum temperatures were `r round(min(temp_vec), digits = 1)`and `r round(max(temp_vec), digits = 1)`, respectively. 

Some additional values of note include average wind speed at `r round(mean(wind_speed_vec), digits = 1)` mph, and average visibility at `r round(mean(visib_vec), digits = 1)` miles.

## Time for plotting!

```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + 
  geom_point() +
  labs(y = "Temp (F)" , x = "Hourly Time of Recording", title = "Hourly Temperature and Humidity during Jan 2013")

ggsave("scatterplot.pdf")
```

Figure 1: Hourly Temperature and Humidity during Jan 2013. While regular fluctuations in temperature occurred, an overall increase in temperature was observed from early to mid-January. Relative humidity was low, and then considerably increased near mid-January. 

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.